Developing a preprint culture in biology

### 2013-02-27 ms.tex
Add Ram's paper

This manuscript was developed entirely as an open project on GitHub. GitHub is
one of several hosting services for collaborative development using the Git
version control system (VCS). It allows numerous contributers to work
asynchronously on the same project, often in parallel branches, all of which can
be effortlessly merged and version controlled.  Git is primarily used for
software development \cite{aru12} but it provides a powerful tool way to
collaborate on every step of the manuscript development process.

>>>>

This manuscript was developed entirely as an open project on GitHub. GitHub is
one of several hosting services for collaborative development using the Git
version control system (VCS). It allows numerous contributers to work
asynchronously on the same project, often in parallel branches, all of which can
be effortlessly merged and version controlled.  Git is primarily used for
software development \cite{aru12} but it provides a powerful tool way to
collaborate on every step of the manuscript development process \cite{ram13}.
